\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.35in]{geometry}
\usepackage{multicol,amsmath,amssymb,bm}
\usepackage{setspace}
\usepackage{titlesec}
\setstretch{0.9}
\pagenumbering{gobble}
\setlength{\parskip}{1pt}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{10pt}
\titlespacing*{\section}{0pt}{2pt}{2pt}

\begin{document}
\small
\begin{multicols*}{2}
\raggedright

\textbf{\Large NETWORKS QUIZ CHEAT SHEET}\\[-2pt]
\hrulefill

\section*{1. Streaming \& CDNs}
\textbf{Chunk:} small video segments (2–10s) encoded at multiple bitrates (ABR: Adaptive Bitrate).  
\textbf{Manifest (MPD):} text file listing chunk URLs, bitrates, durations.  
\textbf{Initial playout delay:}
\[
d_0 = \max_i [a_i - (a_1 + (i-1)T)]
\]
$a_i$: arrival time; $T$: chunk duration. Choose $d_0$ large enough so every chunk arrives before playback.  
\textbf{CDN (Content Delivery Network):} distributed edge servers storing replicas near users $\Rightarrow$ low RTT, load balancing, redundancy.  
\textbf{False:} not P2P among users.  
\textbf{ABR:} client picks next chunk bitrate based on buffer \& throughput.

\section*{2. 802.11 Wireless (Wi-Fi)}
\textbf{CSMA/CA:} Carrier Sense Multiple Access w/ Collision Avoidance (half-duplex radios $\Rightarrow$ can’t detect while transmitting).  
\textbf{SIFS $<$ DIFS:} ensures ACK/CTS priority.  
\textbf{ACK:} sent after SIFS.  
\textbf{Hidden terminal:} A,C $\not\!\leftrightarrow$ each other but both $\to$ B $\Rightarrow$ collision at B.  
\textbf{Exposed terminal:} B$\to$A makes C silent even though C$\to$D fine.  
\textbf{RTS/CTS:} handshake to reduce hidden collisions.  
Flow: RTS$\to$CTS$\to$DATA$\to$ACK.  
\textbf{NAV (Network Allocation Vector):} timer that reserves channel for duration.  
\textbf{RTS/CTS limits:} fails if simultaneous RTS, lost CTS/ACK; use for large frames or high collision rate.

\section*{3. Reliable Data Transfer (ARQ)}
\textbf{ARQ:} Automatic Repeat reQuest (resend on loss).  
\textbf{ACK/NACK:} Acknowledge or Negative Acknowledge.  
\textbf{GBN (Go-Back-N):}
\begin{itemize}\itemsep0pt
\item Window: $W \le 2^k - 1$
\item Receiver accepts in-order only; cumulative ACK = last in-order pkt
\item On timeout: retransmit all unacked pkts (base$\ldots$next-1)
\end{itemize}
\textbf{SR (Selective Repeat):}
\begin{itemize}\itemsep0pt
\item Window: $W \le 2^{k-1}$
\item Receiver buffers out-of-order; ACKs each pkt
\item On timeout: retransmit only missing pkt
\end{itemize}
\textbf{Lost pkt:}  
GBN $\Rightarrow$ resend from loss onward.  
SR $\Rightarrow$ only lost ones resent.  
\textbf{Lost ACK:} timeout triggers resend (GBN: all, SR: missing).  
\textbf{Receiver window:} $[next\_expected, next\_expected+W-1]$.  
\textbf{Cumulative ACK:} last in-order seq num.  

\section*{4. Ethernet (Wired)}
\textbf{CSMA/CD:} Carrier Sense Multiple Access w/ Collision Detection.  
\textbf{Collision detection rule:}
\[
t_{frame} \ge 2\tau
\]
$\tau$: one-way propagation delay.  
\textbf{Min frame size:} 64 bytes (512 bit-times @10Mb/s = 51.2$\mu$s).  
Ensures collision detected before send finishes.  
\textbf{Slot time:} 512 bit-times = 64B.  
\textbf{Binary Exponential Backoff:} wait random time $\in[0,2^k-1]\times$slot\_time after collision.

\section*{5. Wi-Fi vs Ethernet}
\begin{tabular}{p{1.1cm}p{2.9cm}}
\textbf{Ethernet:} & CSMA/CD, full-duplex, detects collisions.\\
\textbf{Wi-Fi:} & CSMA/CA, half-duplex, avoids collisions.\\
\end{tabular}\\[2pt]
Wi-Fi uses ACKs, RTS/CTS, and interframe spacing; Ethernet uses none.  
Reason Wi-Fi $\neq$ CD: can’t hear while sending (strong self-interference).

\section*{6. Constants \& Key Formulas}
\begin{itemize}\itemsep0pt
\item $d_0 = \max_i [a_i - (a_1 + (i-1)T)]$
\item GBN: $W \le 2^k - 1$ \quad SR: $W \le 2^{k-1}$
\item Ethernet slot time: 512 bit-times (64B)
\item 802.11: SIFS $<$ DIFS
\item TCP ACK num = next expected byte
\item Hidden = collide @ receiver; Exposed = blocked needlessly
\end{itemize}

\section*{7. Acronyms \& Definitions}
\begin{tabular}{@{}p{1.2cm}p{3.5cm}@{}}
ABR & Adaptive Bitrate (adjusts quality dynamically)\\
ACK & Acknowledgment (pkt received)\\
ARQ & Automatic Repeat reQuest (retransmit loss)\\
CDN & Content Delivery Network (edge caching)\\
CSMA & Carrier Sense Multiple Access\\
CSMA/CD & ...with Collision Detection (Ethernet)\\
CSMA/CA & ...with Collision Avoidance (Wi-Fi)\\
CTS & Clear to Send (reply to RTS)\\
DIFS & Distributed InterFrame Space\\
GBN & Go-Back-N (ARQ type)\\
MPD & Media Presentation Description (manifest)\\
NAV & Network Allocation Vector (reserve time)\\
RTS & Request to Send (ask to send)\\
SIFS & Short InterFrame Space (ACK/CTS gap)\\
SR & Selective Repeat (per-packet ACK)\\
RTT & Round Trip Time (send + reply)\\
$\tau$ & Propagation delay (one-way)\\
$W$ & Window size (in-flight pkts)\\
\end{tabular}

\section*{8. Quick Recall}
\textbf{Why 64B min frame?} detect collision within $2\tau$.\\
\textbf{Why CSMA/CA not CD?} half-duplex radios.\\
\textbf{RTS/CTS helps?} hidden yes, exposed no.\\
\textbf{GBN vs SR?} GBN resends all, SR resends missing.\\
\textbf{Formula for $d_0$?} max arrival–schedule lag.\\
\textbf{SIFS $<$ DIFS?} ACK/CTS priority.\\

\end{multicols*}
\end{document}
